Appendix 2: Additional R packages

### 2020-10-18 ms/appendix2.tex
pre-release

@@

bibtex & 0.4.2.2 & Francois (2020)\tabularnewline

@@

cli & 2.0.2 & Cs\a'ardi (2020)\tabularnewline

@@

cowplot & 1.0.0 & Wilke (2019)\tabularnewline

@@

dplyr & 1.0.0 & Wickham et al. (2020a)\tabularnewline
ellipsis & 0.3.1 & Wickham (2020)\tabularnewline

@@

furrr & 0.1.0 & Vaughan and Dancho (2018)\tabularnewline
future & 1.18.0 & Bengtsson (2020)\tabularnewline

@@

globals & 0.12.5 & Bengtsson (2019a)\tabularnewline
glue & 1.4.1 & Hester (2020)\tabularnewline

@@

httr & 1.4.1 & Wickham (2019b)\tabularnewline
jsonlite & 1.7.0 & Ooms (2014)\tabularnewline

@@

knitr & 1.29 & Xie (2020a)\tabularnewline

@@

listenv & 0.8.0 & Bengtsson (2019b)\tabularnewline

@@

MASS & 7.3-51.6 & Venables and Ripley (2002)\tabularnewline

@@

readr & 1.3.1 & Wickham et al. (2018)\tabularnewline

@@

rlang & 0.4.7 & Henry and Wickham (2020b)\tabularnewline
rmarkdown & 2.3 & Allaire et al. (2020a)\tabularnewline

@@

rticles & 0.14 & Allaire et al. (2020b)\tabularnewline

@@

stringi & 1.4.6 & Gagolewski (2020)\tabularnewline
stringr & 1.4.0 & Wickham (2019c)\tabularnewline
tibble & 3.0.3 & Müller and Wickham (2020b)\tabularnewline
tidyr & 1.1.0 & Wickham and Henry (2020)\tabularnewline

@@

@@

vctrs & 0.3.1 & Wickham et al. (2020b)\tabularnewline
withr & 2.2.0 & Hester et al. (2020)\tabularnewline
xfun & 0.15 & Xie (2020b)\tabularnewline

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-allaire2020rmarkdown}{}%
Allaire, J., Xie, Y., McPherson, J., Luraschi, J., Ushey, K., Atkins,
A., Wickham, H., Cheng, J., Chang, W., and Iannone, R. (2020a).
\emph{Rmarkdown: Dynamic documents for r}. Available at:
\url{https://github.com/rstudio/rmarkdown}.

@@

\leavevmode\hypertarget{ref-bengtsson2020future}{}%
Bengtsson, H. (2020). \emph{Future: Unified parallel and distributed
processing in r for everyone}. Available at:
\url{https://CRAN.R-project.org/package=future}.

\leavevmode\hypertarget{ref-bengtsson2019globals}{}%
Bengtsson, H. (2019a). \emph{Globals: Identify global objects in r
expressions}. Available at:
\url{https://CRAN.R-project.org/package=globals}.

\leavevmode\hypertarget{ref-bengtsson2019listenv}{}%
Bengtsson, H. (2019b). \emph{Listenv: Environments behaving (almost) as
lists}. Available at: \url{https://CRAN.R-project.org/package=listenv}.

@@

\leavevmode\hypertarget{ref-vaughan2018furrr}{}%
Vaughan, D., and Dancho, M. (2018). \emph{Furrr: Apply mapping functions
in parallel using futures}. Available at:
\url{https://CRAN.R-project.org/package=furrr}.

\leavevmode\hypertarget{ref-venables2002modern}{}%
Venables, W. N., and Ripley, B. D. (2002). \emph{Modern applied
statistics with s}. Fourth. New York: Springer Available at:
\url{http://www.stats.ox.ac.uk/pub/MASS4}.

@@

\leavevmode\hypertarget{ref-wickham2020ellipsis}{}%
Wickham, H. (2020). \emph{Ellipsis: Tools for working with ...}
Available at: \url{https://CRAN.R-project.org/package=ellipsis}.

@@

\leavevmode\hypertarget{ref-wickham2019httr}{}%
Wickham, H. (2019b). \emph{Httr: Tools for working with urls and http}.
Available at: \url{https://CRAN.R-project.org/package=httr}.

\leavevmode\hypertarget{ref-wickham2019stringr}{}%
Wickham, H. (2019c). \emph{Stringr: Simple, consistent wrappers for
common string operations}. Available at:
\url{https://CRAN.R-project.org/package=stringr}.

@@

\leavevmode\hypertarget{ref-wickham2020dplyr}{}%
Wickham, H., François, R., Henry, L., and Müller, K. (2020a).
\emph{Dplyr: A grammar of data manipulation}. Available at:
\url{https://CRAN.R-project.org/package=dplyr}.

\leavevmode\hypertarget{ref-wickham2020tidyr}{}%
Wickham, H., and Henry, L. (2020). \emph{Tidyr: Tidy messy data}.
Available at: \url{https://CRAN.R-project.org/package=tidyr}.

@@

\leavevmode\hypertarget{ref-wickham2018readr}{}%
Wickham, H., Hester, J., and Francois, R. (2018). \emph{Readr: Read
rectangular text data}. Available at:
\url{https://CRAN.R-project.org/package=readr}.

@@

\leavevmode\hypertarget{ref-wilke2019cowplot}{}%
Wilke, C. O. (2019). \emph{Cowplot: Streamlined plot theme and plot
annotations for 'ggplot2'}. Available at:
\url{https://CRAN.R-project.org/package=cowplot}.

@@

\leavevmode\hypertarget{ref-xie2020xfun}{}%
Xie, Y. (2020b). \emph{Xfun: Miscellaneous functions by 'yihui xie'}.
Available at: \url{https://CRAN.R-project.org/package=xfun}.

@@

@@

\leavevmode\hypertarget{ref-zeileis2009escaping}{}%
Zeileis, A., Hornik, K., and Murrell, P. (2009). Escaping RGBland:
Selecting colors for statistical graphics. \emph{Computational
Statistics \& Data Analysis} 53, 3259--3270.
doi:\href{https://doi.org/10.1016/j.csda.2008.11.033}{10.1016/j.csda.2008.11.033}.

>>>>

\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newenvironment{cslreferences}%
  {\setlength{\parindent}{0pt}%
  \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}%
  {\par}

@@

bibtex & 0.4.2.3 & Francois (2020)\tabularnewline

@@

cli & 2.1.0 & Cs\a'ardi (2020)\tabularnewline

@@

cowplot & 1.1.0 & Wilke (2020)\tabularnewline

@@

dplyr & 1.0.2 & Wickham et al. (2020a)\tabularnewline
ellipsis & 0.3.1 & Wickham (2020a)\tabularnewline

@@

furrr & 0.2.0 & Vaughan and Dancho (2020)\tabularnewline
future & 1.19.1 & Bengtsson (2020a)\tabularnewline

@@

globals & 0.13.1 & Bengtsson (2020b)\tabularnewline
glue & 1.4.2 & Hester (2020)\tabularnewline

@@

httr & 1.4.2 & Wickham (2020b)\tabularnewline
jsonlite & 1.7.1 & Ooms (2014)\tabularnewline

@@

knitr & 1.30 & Xie (2020a)\tabularnewline

@@

listenv & 0.8.0 & Bengtsson (2019)\tabularnewline

@@

MASS & 7.3-53 & Venables and Ripley (2002)\tabularnewline

@@

readr & 1.4.0 & Wickham and Hester (2020)\tabularnewline

@@

rlang & 0.4.8 & Henry and Wickham (2020b)\tabularnewline
rmarkdown & 2.4 & Allaire et al. (2020a)\tabularnewline

@@

& & Xie et al. (2020)\tabularnewline
rticles & 0.16 & Allaire et al. (2020b)\tabularnewline

@@

stringi & 1.5.3 & Gagolewski (2020)\tabularnewline
stringr & 1.4.0 & Wickham (2019b)\tabularnewline
tibble & 3.0.4 & Müller and Wickham (2020b)\tabularnewline
tidyr & 1.1.2 & Wickham (2020c)\tabularnewline

@@

tinytex & 0.26 & Xie (2020b)\tabularnewline
& & Xie (2019)\tabularnewline

@@

vctrs & 0.3.4 & Wickham et al. (2020b)\tabularnewline
withr & 2.3.0 & Hester et al. (2020)\tabularnewline
xfun & 0.18 & Xie (2020c)\tabularnewline

@@

\hypertarget{refs}{}
\begin{cslreferences}
\leavevmode\hypertarget{ref-allaire2020rmarkdown}{}%
Allaire, J., Xie, Y., McPherson, J., Luraschi, J., Ushey, K., Atkins,
A., Wickham, H., Cheng, J., Chang, W., and Iannone, R. (2020a).
\emph{Rmarkdown: Dynamic documents for r}. Available at:
\url{https://github.com/rstudio/rmarkdown}.

@@

\leavevmode\hypertarget{ref-bengtsson2020unifying}{}%
Bengtsson, H. (2020a). A unifying framework for parallel and distributed
processing in r using futures. Available at:
\url{https://arxiv.org/abs/2008.00553}.

\leavevmode\hypertarget{ref-bengtsson2020globals}{}%
Bengtsson, H. (2020b). \emph{Globals: Identify global objects in r
expressions}. Available at:
\url{https://CRAN.R-project.org/package=globals}.

\leavevmode\hypertarget{ref-bengtsson2019listenv}{}%
Bengtsson, H. (2019). \emph{Listenv: Environments behaving (almost) as
lists}. Available at: \url{https://CRAN.R-project.org/package=listenv}.

@@

\leavevmode\hypertarget{ref-vaughan2020furrr}{}%
Vaughan, D., and Dancho, M. (2020). \emph{Furrr: Apply mapping functions
in parallel using futures}. Available at:
\url{https://CRAN.R-project.org/package=furrr}.

\leavevmode\hypertarget{ref-venables2002modern}{}%
Venables, W. N., and Ripley, B. D. (2002). \emph{Modern applied
statistics with s}. Fourth. New York: Springer Available at:
\url{http://www.stats.ox.ac.uk/pub/MASS4/}.

@@

\leavevmode\hypertarget{ref-wickham2020ellipsis}{}%
Wickham, H. (2020a). \emph{Ellipsis: Tools for working with ...}
Available at: \url{https://CRAN.R-project.org/package=ellipsis}.

@@

\leavevmode\hypertarget{ref-wickham2020httr}{}%
Wickham, H. (2020b). \emph{Httr: Tools for working with urls and http}.
Available at: \url{https://CRAN.R-project.org/package=httr}.

\leavevmode\hypertarget{ref-wickham2019stringr}{}%
Wickham, H. (2019b). \emph{Stringr: Simple, consistent wrappers for
common string operations}. Available at:
\url{https://CRAN.R-project.org/package=stringr}.

@@

\leavevmode\hypertarget{ref-wickham2020tidyr}{}%
Wickham, H. (2020c). \emph{Tidyr: Tidy messy data}. Available at:
\url{https://CRAN.R-project.org/package=tidyr}.

\leavevmode\hypertarget{ref-wickham2020dplyr}{}%
Wickham, H., François, R., ? Henry, L., and Müller, K. (2020a).
\emph{Dplyr: A grammar of data manipulation}. Available at:
\url{https://CRAN.R-project.org/package=dplyr}.

@@

\leavevmode\hypertarget{ref-wickham2020readr}{}%
Wickham, H., and Hester, J. (2020). \emph{Readr: Read rectangular text
data}. Available at: \url{https://CRAN.R-project.org/package=readr}.

@@

\leavevmode\hypertarget{ref-wilke2020cowplot}{}%
Wilke, C. O. (2020). \emph{Cowplot: Streamlined plot theme and plot
annotations for 'ggplot2'}. Available at:
\url{https://CRAN.R-project.org/package=cowplot}.

@@

\leavevmode\hypertarget{ref-xie2019tinytex}{}%
Xie, Y. (2019). TinyTeX: A lightweight, cross-platform, and
easy-to-maintain latex distribution based on tex live. \emph{TUGboat},
30--32. Available at:
\url{http://tug.org/TUGboat/Contents/contents40-1.html}.

\leavevmode\hypertarget{ref-xie2020tinytex}{}%
Xie, Y. (2020b). \emph{Tinytex: Helper functions to install and maintain
tex live, and compile latex documents}. Available at:
\url{https://github.com/yihui/tinytex}.

\leavevmode\hypertarget{ref-xie2020xfun}{}%
Xie, Y. (2020c). \emph{Xfun: Miscellaneous functions by 'yihui xie'}.
Available at: \url{https://CRAN.R-project.org/package=xfun}.

@@

\leavevmode\hypertarget{ref-xie2020markdown}{}%
Xie, Y., Dervieux, C., and Riederer, E. (2020). \emph{R markdown
cookbook}. Boca Raton, Florida: Chapman; Hall/CRC Available at:
\url{https://bookdown.org/yihui/rmarkdown-cookbook}.

@@

\leavevmode\hypertarget{ref-zeileis2009escaping}{}%
Zeileis, A., Hornik, K., and Murrell, P. (2009). Escaping RGBland:
Selecting colors for statistical graphics. \emph{Computational
Statistics \& Data Analysis} 53, 3259--3270.
doi:\href{https://doi.org/10.1016/j.csda.2008.11.033}{10.1016/j.csda.2008.11.033}.
\end{cslreferences}
